Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-05 paper.qmd
Updated Figure 12

@@

```{r}
#| label: tsne-pbmc-read-best
tsne_pbmc <- read_rds("data/pbmc3k/pbmc_tsne_30.rds")
pbmc_scaled_obj <- gen_scaled_data(
  data = tsne_pbmc)
tsne_pbmc_scaled_best <- pbmc_scaled_obj$scaled_nldr

>>>>

df_bin_centroids_pbmc <- df_bin_centroids_pbmc |>
  dplyr::filter(std_counts > 0)

@@

```{r}
#| label: tsne-pbmc-read-best
tsne_pbmc <- read_rds("data/pbmc3k/pbmc_tsne_30.rds")
```
